\documentclass[11pt,letterpaper]{article}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[default]{opensans}
    \usepackage{titlesec}
    \usepackage{enumitem}
    \usepackage{multicol}
    \usepackage{geometry}
    \usepackage{amssymb}
    \pagestyle{empty}
    \raggedright
    \usepackage{hyperref}
    
% set title so correct title displays for any filename
\hypersetup{
    pdfauthor={Kevin Wu},
    pdftitle={Kevin Wu Resume},
}
    
\hypersetup{
    colorlinks=false
}

% ATS parsing
\input{glyphtounicode}
\pdfgentounicode=1

% margins
\geometry{letterpaper, margin=0.5in}

% custom \large and \Huge font sizes
\makeatletter %only needed in preamble
\renewcommand\large{\@setfontsize\large{13pt}{18}}
\renewcommand\Huge{\@setfontsize\Huge{35pt}{18}}
\makeatother

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\titleformat{\section}{
  \vspace*{-13pt}\scshape\large
}{}{0em}{}[\titlerule \vspace{-5pt}]

\newcommand{\resumeItemListStart}{
    \begin{itemize}[itemsep=1pt, parsep=0pt, topsep=0pt]
}

\newcommand{\resumeItemListEnd}{
    \end{itemize}
}

% suppress end of lines with comments (https://texfaq.org/FAQ-spinmacro)
\newcounter{datediff}
\newcommand{\yearsSince}[1]{%
    \setcounter{datediff}{\year}%
    \addtocounter{datediff}{-#1}%
    \thedatediff%
}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%==== Profile ====%

\begin{center}
    {\Huge Kevin Wu}
    
    \vspace{10pt}
    kevin@kevinniuwu.com
    |
    (317) 701-8424
    |
    github.com/Exaphis
    |
    linkedin.com/in/kevw
\end{center}
\vspace{-5pt}

%==== Education ====%
\section{Education}

\textbf{Purdue University} \hfill \textit{Aug. 2019 -- Dec. 2022}

B.S. in Computer Science Honors \hfill GPA: 4.00

B.S. in Mathematics \hfill Dean's List + Semester Honors all semesters

% \textbf{Relevant coursework:} Data Structures/Algorithms, Computer Architecture, Programming in C, Competitive Programming II

% \vspace{2mm}

\section{Skills}

\textbf{Languages:}
Python (\yearsSince{2015}yrs), 
Java (\yearsSince{2017}yrs),
C (\yearsSince{2019}yrs),
C++ (\yearsSince{2019}yrs)

\textbf{Tools/Frameworks:} Git, Django, React, Linux, Unity

%==== Experience ====%
\section{Experience}

\textbf{Citrix} \hfill Burlington, MA (Remote)

% Work log
% - ScanWritableFiles
% - AppRuleCompare
%     - Debugging file read issue
% - Testing the driver on various Windows versions
% - Refactoring registry init
%     - BSODing Win7...
% - Refactoring params list
% - Testing WS2022
% - Fixing bug in log file rotation
% - Adding camsvc exclusion if Windows Store is removed

Software Engineer Intern, App Layering \hfill \textit{May 2021 -- Aug. 2021}

\resumeItemListStart
	\item Created a Windows Shell extension using C++ to show files that are only on a user's writable layer
	\item Improved file list times by 20\% for Citrix's app layer viewer built with C++/MFC using lazy loading
	\item Designed and implemented a data-driven registry value initialization routine using C in the Citrix Composite File System kernel driver
\resumeItemListEnd

\textbf{Google Summer of Code (Debian)} \hfill Remote

Student Developer \hfill \textit{May 2020 -- Aug. 2020}

\resumeItemListStart
	\item Developed and tested Crossgrader, a package to switch the CPU architecture of a Debian installation
	\item Reduced cross-grade times from 6+ hours to 30 minutes using libapt's Python interface
    \item Presented final product at DebConf20; maintained Crossgrader and uploaded Crossgrader to the Debian package archive
\resumeItemListEnd

%==== Personal Projects ====%
\section{Projects}

\textbf{Synchronous} | \emph{JavaScript, React, Python, Django} \hfill \textit{Jan. 2021 -- Present}

\resumeItemListStart
    \item Worked in a team of 4 to create an easy-to-use collaborative workspace app using React and Django
    \item Engineered a RESTful API using the Django REST Framework to handle workspace creation
    \item Created an Etherpad plugin to restore past revisions, which is used in collaborative text documents
\resumeItemListEnd

\textbf{HackQ-Trivia} | \emph{Python, Natural language processing} \hfill \textit{Feb. 2018 -- Present}

\resumeItemListStart
    \item Developed a bot that answers HQ Trivia's questions during live shows in real time
	\item Reverse-engineered HQ's WebSocket-based client-server communication to receive questions
	\item Utilized Python's Natural Language Toolkit to analyze search results and determine most likely answer
	\item Improved question answering speed by 3x using asynchronous HTTP requests
\resumeItemListEnd

\textbf{Tsunami} | \emph{C, C++, Windows Driver Kit} \hfill \textit {Nov. 2018 -- May 2020}

\resumeItemListStart
    \item Programmed a Windows driver that covertly reads and writes a process's memory from kernel space
	\item Implemented discardable section hijacking and page table entry remapping to evade detection
	\item Developed a proof-of-concept wallhack using Tsunami for the first-person shooter game Overwatch
\resumeItemListEnd

%==== Awards ====%
\section{Achievements}

\resumeItemListStart
    \item \textbf{Purdue Corporate Partner Scholarship} \hfill \textit{Apr. 2021}
	\item \textbf{AMCS Spring Coding Challenge} -- 1st place \hfill \textit{Feb. 2020}
	\item \textbf{American Computer Science League All-Star Contest} -- Senior-3 Division 1st place \hfill \textit{May 2019}
	\item \textbf{Purdue ACM Coding Competition} -- 1st place \hfill \textit{Apr. 2019}
\resumeItemListEnd
	
\end{document}